Comparing tool variability and numerical variability in fMRI analyses

### 2021-09-28 paper/paper.tex
Fix colorbar resolution

\newcommand{\fslspm}{FSL-SPM\xspace}
\newcommand{\fslafni}{FSL-AFNI\xspace}
\newcommand{\afnispm}{AFNI-SPM\xspace}
\newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:} #1\color{black}\xspace}

@@

A summary of the statistic values from the group-level (un)thresholded T-statistics is conducted in
Table~\ref{table:pipeline-stats}.
The variability between pair of images in each condition was measured using the mean and standard deviation of absolute differences.
Overall, the distribution of the pairwise variations in WT is an order of magnitude lower than BT in both means and standard deviations.
While the most variability was observed in the pair of \fslafni, the pair of \fslspm made the least variations for all conditions.
% Overally, we see that values in between tools are comparable to values in within tool results.

@@

% Fig4
The scatter plot in Figure~\ref{fig:correlations} represents the correlation of standard deviation in WT and BT variability.
We found two major clusters, including the identity cluster that corresponds to the correlations
between BT and WT with the ratio of $0.5 < BT/WT < 1.5$ where the standard deviations are bigger than 0.1,
and the upper cluster that shows voxels where BT $\approx$ 0.
The percentage of voxels included in the identity cluster is \%9.9 in \fslspm, \%17.3 in \fslafni, and \%13.8 in \afnispm,
and in the upper cluster is $\approx$ \%1 for each pair of tools.
The identity area is also represented on the MNI space in the second row in Figure~\ref{fig:correlations}.
This figure shows the spatial localization of the parts of the brain that BT variability is correlated with the numerical variability.
This refines the presented results in Figure~\ref{fig:unthresh-varmaps},
which indicates how correlation is uniformly distributed across the brain.

>>>>

\newcommand{\fslspm}{FSL-SPM\xspace}
\newcommand{\fslafni}{FSL-AFNI\xspace}
\newcommand{\afnispm}{AFNI-SPM\xspace}
\newcommand{\tristan}[1]{\color{orange}\textbf{From Tristan:} #1\color{black}\xspace}
\newcommand{\note}[2]{\color{green}\textbf{Note:} #1\color{black}\xspace}

@@

A summary of the statistic values from the group-level (un)thresholded T-statistics is conducted in
Table~\ref{table:pipeline-stats}.
The variability between pair of images in each condition was measured using the mean and standard deviation of absolute differences.
Overall, the distribution of the pairwise variations in WT is an order of magnitude lower than BT in both means and standard deviations.
While the most variability was observed in the pair of \fslafni, the pair of \fslspm made the least variations for all conditions.
% Overally, we see that values in between tools are comparable to values in within tool results.
\note{Add statistics for subject level (first-level) analyses}

@@

% Fig4
The scatter plot in Figure~\ref{fig:correlations} represents the correlation of standard deviation in WT and BT variability.
We found two major clusters, including the identity cluster that corresponds to the correlations
between BT and WT with the ratio of $0.5 < BT/WT < 2$ where the standard deviations are bigger than 0.1,
and the upper cluster that shows voxels where BT $\approx$ 0.
The percentage of voxels included in the identity cluster is \%9.9 in \fslspm, \%17.3 in \fslafni, and \%13.8 in \afnispm,
and in the upper cluster is $\approx$ \%1 for each pair of tools.
The identity area is also represented on the MNI space in the second row in Figure~\ref{fig:correlations}.
This figure shows the spatial localization of the parts of the brain that BT variability is correlated with the numerical variability.
This refines the presented results in Figure~\ref{fig:unthresh-varmaps},
which indicates how correlation is uniformly distributed across the brain.
